\plaintitle

### 2016-08-29 drafts/labor/introduction.tex
friday changes committed sunday

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother

\begin{document}

% what am i trying to say? that crowd work is an instantiation of piecework
% framing/bullet points

\section{Introduction}
\topic{The past decade has seen a flourishing of on--demand work,
motivated by the framing of work as
contextually abstract and therefore
interchangeable and modular.}
The statuses of many of these workers
(known colloquially as ``Turkers'')
have become so fleeting that 
they have been described as ``transient''
\cite{kargerIterativeLearning,mitraComparingStrategies,latozaCrowdDev}.
The realization
that tasks can be accomplished by directing and managing this crowd of workers
has spurred the research and and industry communities to flock to sites of labor
like Amazon's Mechanical Turk (AMT)
to explore the limits of this distributed, seemingly ephemeral labor force.
Researchers in particular have taken to the space in earnest,
finding opportunities to enable new forms of work
as well as using Turkers
as representative populations of the public
\cite{bernsteinSoylent,redballoon,paolacci2010running}.

The many sites of work replicating and extending on
the general style of labor popularized by AMT
have predominantly involved work done on a computer
or involving the human processing of data,
leading many to call this ``information work"
\cite{turkopticon,professionalCrowdworkEthics,IraniFromCriticalDesign,OlsonMakeDistanceWorkWork}.
\citeauthor{howe2008crowdsourcing} defined ``crowdsourcing'' in \citeyear{howe2008crowdsourcing}
as
``taking a job traditionally performed by a designated agent
(usually an employee)
and outsourcing it to an undefined,
generally large group of people in the form of an open call''
\cite{howe2008crowdsourcing}.

In the years since,
scholars have generated taxonomies for the work done by many distributed workers
in an attempt to better categorize and reason about the many forms of work done 
on information work platforms such as AMT, oDesk, etc\dots
\cite{yuenSurvey,geiger2011managing,quinnbedersonTaxonomy}.
We add that,
under \citeauthor{howe2008crowdsourcing}'s constraints,
even \textit{more} new forms of work fall squarely under
the metaphorical umbrella we collectively call ``crowdsourcing''.

\topic{This matters because\dots}
Indeed, this on--demand workforce has sparked interest
across industries ranging
driving for hire (for example Uber),
house--cleaning (Handy),
and generalized services (TaskRabbit)
\cite{uberOfficial,zaarlyOfficial,taskrabbitOfficial}.
Today, a rapidly growing transient workforce is forming,
itself assembling piece--by--piece as industries and researchers find yet more unexpected ways
to benefit from a latent pool of previously vetted workers
\cite{pewSharing}.

Researchers have made efforts to understand the people
that have gravitated toward crowdsourcing platforms
since its emergence and popularization,
but as the form of work has grown and changed, so too have the demographics of workers
\cite{Ross,whoareNOTtheTurkers}.
Some of this research has been motivated by the realization of the sociality of gig work,
and the frustration and disenfranchisement that these systems embody
\cite{turkopticon,dynamo}.
Other work has focused on the outcomes of work,
reflecting on the resistance workers express against digitally mediated labor markets
\cite{uberAlgorithm}.

The extant body of work has ostensibly sought to answer one underlying question:
What does the future hold for work and those that do it? % expand on ...?
Researchers have offered their input on this open question along three major threads of scholarship:
\begin{enumerate}
  \item What are the limits of crowdsourcing?
  Perhaps more tightly constrained,
  what can and cannot be done by crowd workers?
    \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,embracingErrorKrishna,
          Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364};
  \item What forms of work design, and worker management and arrangement, are viable?
    \cite{bernsteinSoylent,sensitiveTasks,LykourentzouPersonalityMatters,KucherbaevReLauncher,
          Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,
          Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item What will work and the place of work look like for the workers?
    \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,whyWouldAnyoneBrewer,
          takingAHITMcInnis}
\end{enumerate}

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
  % \theendnotes
\nobalance{}
\clearpage
\begin{appendices}
\section{Sleeping kittens}
\begin{itemize}
  \item on--demand labor has consumed an increasing proportion of the labor market in the past ten years [\textit{Pew research on on--demand labor}];
  the work  has ranged from Turk work processes
  \item some of it has been about resisting Uber \& other gig labor platforms \cite{bernsteinSoylent,uberAlgorithm};
  some researchers have tackled understanding this new instantiation of work, but come up short (\textit{how}).

  \item (what binds this together)
  \item we offer a framing on this topic that situates the research so far on a timeline of the maturation of another form of work that emerged approximately 150 years ago
  --- that is, piecework --- which convincingly suggests that on--demand labor in the form of Turking, driving for Uber, etc\dots are in fact little more than piecework re--surging today.

  \item this paper will trace the body of research describing microwork --- and later gig work --- and place it in the context of historical piecework and the industrial revolution as a whole.
  \item informed by this new lens, we'll then turn our attention to the future of this re--emergent form of work, and suggest ways that researchers and users of on--demand labor might influence the outcomes we predict in this paper.
\end{itemize}
\end{appendices}

>>>>

\documentclass[trackingWork]{subfiles}
\onlyinsubfile{
  \hypersetup{
    citecolor  = blue,
    linkcolor  = JokeGreen,
  }
}

\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\section{Introduction}
\topic{The past decade has seen a flourishing of on--demand work,
largely driven by the reformulation of work as
the constituent parts of larger tasks.}
This framing of work into abstract blocks
has allowed people to engage in work despite
limited time,
little to no awareness of the broader context of the work, and 
(often) fleeting identities and associations
\cite{kargerIterativeLearning,mitraComparingStrategies,latozaCrowdDev}.
The realization
that complex tasks can be accomplished by directing and managing crowds of workers
has spurred the research and and industry communities to flock to sites of labor
like Amazon's Mechanical Turk (AMT)
to explore the limits of this distributed, fleeting workforce.
Researchers in particular have taken to the space in earnest,
finding opportunities to enable new forms of work
using this population of ``Turkers''
\note{as test subjects in a sort of at--scale laboratory for economic and other behavioral studies}
\cite{bernsteinSoylent,redballoon,paolacci2010running}.

\topic{This form of work has grown considerably in size,
far beyond the domain of ``information work'' from which it first sprang.}
While \citeauthor{howe2008crowdsourcing} described crowdsourcing as
``outsourcing [work] to an undefined, generally large group of people in the form of an open call'',
for years the instantiation of this work was limited to the utilization of
human intelligence to process data and act on information
\cite{CrowdsourcingUserStudies,movieSummarizationWu,
      yuenSurvey,geiger2011managing,quinnbedersonTaxonomy}.
More recently, crowdsourcing of embodied work
--- driving, cleaning, for instance ---
has become a focus of on--demand labor markets
\cite{uberAlgorithm,uberOfficial,zaarlyOfficial,taskrabbitOfficial}.
Today, on--demand work promises to become a \joke{yuge industry}
\joke{[citation needed]}.

% \topic{This matters because\dots WHYYYYYYYYYYYYYYY\\}
% Indeed, this on--demand workforce has sparked interest
% across industries ranging
% driving for hire (for example Uber),
% house--cleaning (Handy),
% and generalized services (TaskRabbit)
% \cite{uberOfficial,zaarlyOfficial,taskrabbitOfficial}.
% Today, a rapidly growing transient workforce is forming,
% itself assembling piece--by--piece as industries and researchers find yet more unexpected ways
% to benefit from a latent pool of previously vetted workers
% \cite{pewSharing}.

\topic{For all the growth we've observed in this labor market,
we have also seen a complicated and conflicted culture emerge among its constituent workers.}
Researchers have made efforts to understand the people
that have gravitated toward crowdsourcing platforms
since its emergence and popularization,
but as the form of work has grown and changed, so too have the demographics of workers
\cite{Ross,whoareNOTtheTurkers}.
Some of this research has been motivated by the identification of the sociality of gig work,
and the frustration and disenfranchisement that these systems embody
\cite{turkopticon,dynamo}.
Other work has focused on the \textit{outcomes} of this frustration,
reflecting on the resistance workers express against digitally mediated labor markets
\cite{uberAlgorithm}.

\topic{The extant body of work has ostensibly sought to answer one underlying question:
What does the future hold for work and those that do it?}
Researchers have offered their input on this open question along three major threads:
\begin{enumerate}
  \item What are the limits of crowdsourcing
        \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,embracingErrorKrishna,
              Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364}?
        \note{Perhaps to be more precise, we ask two questions here:
                \begin{enumerate}
                  \item how far will crowdsourcing reach into the everyday lives of people, and
                  \item how complex can crowdwork become?
                \end{enumerate}}
  \item What forms of work design, and worker management and arrangement, are viable?
        \cite{bernsteinSoylent,sensitiveTasks,LykourentzouPersonalityMatters,KucherbaevReLauncher,
              Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,
              Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item What will work and the place of work look like for the workers?
        \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,whyWouldAnyoneBrewer,
              takingAHITMcInnis}
\end{enumerate}

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
  \nobalance{}
  \clearpage
  \begin{appendices}
  \section{Sleeping kittens}
  \theendnotes
  \end{appendices}

### 2016-08-29 drafts/labor/trackingWork.tex
friday changes committed sunday

\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles,appendix,endnotes}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth,endnotes,cleveref}
\usepackage[normalem]{ulem}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[T1]{fontenc}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

\newcommand{\onlyinsubfile}[1]{#1}
\newcommand{\notinsubfile}[1]{}
\newcommand{\note}[1]{\footnote{#1}}
\newcommand{\topic}[1]{\textbf{#1}} % if you're in a subfile, bold the \topic sentences
\newcommand{\joke}[1]{{\color{JokeGreen}#1}} % if you're in a subfile, bold the \topic sentences

\begin{document}
\renewcommand{\topic}[1]{#1} % don't do anything with \topic sentences; this is just for drafting 
\renewcommand{\joke}[1]{} % don't do anything with \jokes! Just throw them away!
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\renewcommand{\note}[1]{\onlyinsubfile{\note{#1}}}
\title{\plaintitle}

>>>>

\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles,appendix,endnotes}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth,endnotes,cleveref}
\usepackage[normalem]{ulem}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[T1]{fontenc}
\usepackage[pdflang={en-US},pdftex]{hyperref}

\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

\newcommand{\onlyinsubfile}[1]{#1}
\newcommand{\notinsubfile}[1]{}
\newcommand{\note}[1]{\footnote{#1}}
\newcommand{\topic}[1]{\textbf{#1}} % if you're in a subfile, bold the \topic sentences to make it easier to skim/diagnose logical issues
\newcommand{\joke}[1]{{\color{JokeGreen}#1}} % if you're in a subfile, make the joke JokeGreen colored so people know I'm being funny!
\begin{document}
\renewcommand{\topic}[1]{#1} % don't do anything with \topic sentences; this is just for drafting 
\renewcommand{\joke}[1]{} % don't do anything with \jokes! Just throw them away! (Better to drop it than accidentally include it)
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\renewcommand{\note}[1]{\onlyinsubfile{\note{#1}}}

\title{\plaintitle}
